Python as a machine learning language: experiences from the scikit-learn project

### 2013-06-12 paper.tex
wording

The API is designed to adhere to the following broad principles:
\begin{description}
  \item[Inspection.]
       Constructor parameters
       and parameter values determined by learning algorithms
       are stored as public attributes. All of them are documented in a consistent manner.
       % Gilles: Do we really need to bother the reader with such details?
       % (The Python language does not actually distinguish
       % between public and private attributes of objects,
       % but by convention, any identifier
       % prefixed with an underscore (\texttt{\_})
       % is considered ``a non-public part of the API''; \citealp{pythontut}.)
  \item[Non-proliferation of classes.]
       Learning algorithms are objects of custom classes,
       but datasets and hyperparameter names and values
       are represented as standard Python, NumPy or SciPy classes
       rather than new ones whenever feasible.
       % Gilles: I don't understand the phrase below
       % Custom classes adhere to Python conventions and protocols
       % for constructs such as iteration over the folds
       % in a $k$-fold cross validation.
       This should keep \sklearn easy to use
       and easy to combine with other libraries.
       % XXX do we need to elaborate more on this, or do we expect everyone
       % to be an experienced Java/adapter pattern hater?
  \item[Composition.]
       Many machine learning tasks are expressible
       as sequences or combinations of transformations to data.
       Some learning algorithms are also naturally viewed
       as meta-algorithms parameterized on other algorithms.
       To be able to implement and use these algorithms in a simple way,
       all learners are usable with a consistent set of methods
       and a simple syntax is implemented
       for setting and retrieving parameters of sub-estimators.
       % XXX need to describe this!
  \item[Sensible defaults.]
       Whenever an operation requires a user-defined parameter,
       a default and appropriate value is defined by the library.
       The default value should cause the operation to be performed
       in a sensible way (giving a baseline solution for the task at hand).
\end{description}

>>>>

The API is designed to adhere to the following broad principles:
\begin{description}
  \item[Inspection.]
       Constructor parameters
       and parameter values determined by learning algorithms
       are stored as public attributes. All of them are documented in a consistent manner.
       % Gilles: Do we really need to bother the reader with such details?
       % (The Python language does not actually distinguish
       % between public and private attributes of objects,
       % but by convention, any identifier
       % prefixed with an underscore (\texttt{\_})
       % is considered ``a non-public part of the API''; \citealp{pythontut}.)
  \item[Non-proliferation of classes.]
       Learning algorithms are objects of custom classes,
       but datasets and hyperparameter names and values
       are represented as standard Python, NumPy or SciPy classes
       rather than new ones whenever feasible.
       % Gilles: I don't understand the phrase below
       % Custom classes adhere to Python conventions and protocols
       % for constructs such as iteration over the folds
       % in a $k$-fold cross validation.
       This should keep \sklearn easy to use
       and easy to combine with other libraries.
       % XXX do we need to elaborate more on this, or do we expect everyone
       % to be an experienced Java/adapter pattern hater?
  \item[Composition.]
       Many machine learning tasks are expressible
       as sequences or combinations of transformations to data.
       Some learning algorithms are also naturally viewed
       as meta-algorithms parameterized on other algorithms.
       To be able to implement and use these algorithms in a simple way,
       all learners (basic or composed) are usable with a consistent set of methods.
       % Gilles: let elaborate later on the syntax
       % and a simple syntax is implemented
       % for setting and retrieving parameters of sub-estimators.
       % XXX need to describe this!
  \item[Sensible defaults.]
       Whenever an operation requires a user-defined parameter,
       a default and appropriate value is defined by the library.
       The default value should cause the operation to be performed
       in a sensible way (giving a baseline solution for the task at hand).
\end{description}
